### 2017-04-06 paper/evaluation.tex
adjusting times

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{llrrl}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.47m & 1.00x\\%
Medium & Apache \textbf{Flink} & 10.02m & 2.57m & 3.90x\\%
Long & Jenkins CI \textbf{Gerrit} Plugin & 76.32m & 40.31m &  1.89x\\%
Medium & Spotify \textbf{Helios} & 3.70m & 1.63m & 2.28x\\%  
Medium & \textbf{Javaslang} & 2.12m & 1.82m & 1.16x\\%
Medium & \textbf{Jcabi} GitHub & 2.75m & 0.30m & \cellcolor{lightgray}9.01x\\%
Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
Medium & Apache \textbf{Log4J2} & 4.73m & 8.21m & \cellcolor{lightgray}0.58x\\%
Medium & Jankotek \textbf{MapDB} & 10.51m & 8.58m & 1.23x\\%
\midrule
\textbf{total} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Abbreviation of project names appear in bold face
  and highest slowdown/speedup appear in gray color.}
\label{tab:speedup}
\end{figure}

@@

The dimension adoption focuses on the usage of parallelism in
open-source projects.  It evaluates (\numRQC) how often open-source
projects use parallelization schemes and (\numRQE) how developers
involved in costly projects, not using parallelization, perceive this
technology.

\begin{itemize}
    \item \numRQC. \textbf{\RQC{}}
\end{itemize}

To answer \numRQC{}, we selected all projects from the \medg{} and
\longg{} groups, \ie, projects that ran in at least one minute.  This
set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
looked for dynamic and static manifestations of parallelism.

%% The
%% following section report results for each of these cases.

\vspace{1ex}
\subsubsection{Dynamic checking}
\label{sec:rqC-1}

To find dynamic evidence of parallelism, we ran the test suites from
our set of \numMedLong{} projects to output all key-value pairs of
Maven parameters.  To that end, we used the option~\CodeIn{-X} to
produce debug output and the option~\CodeIn{-DskipTests} to skip
execution of tests.  We observed that only bootstrapping the Maven
process suffices to discover which parallel configuration modes it
will use to run tests.  According to Maven's
documentation~\cite{maven-surefire-plugin}, a parallel configuration
depends either on (1) the parameter \CodeIn{parallel} to define the
parallelism mode within a JVM followed by the parameter
\CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
  in old versions of Maven Surefire} to define the number of forked
JVMs.  As such, we captured, for each project, all related key-value
pairs of Maven parameters and mapped those pairs to one of the
possible parallelization modes.  For instance, if a given project
contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel}.  If the parameter
\CodeIn{parallel} is set to \CodeIn{methods} the detected mode will be
\ForkParMeth{}.  Large projects may contain several test suites
distributed on different Maven modules potentially using different
configurations.  For those cases, we collected the Maven output from
each module discarding duplicates as to avoid inflating results. For
instance, if a project contains two modules using the same
configuration, we counted only one occurrence.

\Mar{---- estou aqui}

@@

\subsubsection{Presence of parallelism configurations in build files}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in
\emph{pom.xml} files\Comment{ in the same sample set of \numMedLong{}
projects}. In principle, some projects can use parallel execution
although that is only activated when developers pass certain
parameters to the build process. For instance, it is possible to
create in Maven multiple configurations in the same build file and
select dynamically which one should be used.  We automatically parsed
\Fix{X} build files and we used the same approach to classify the
parsed configurations as in our previous analysis. Initially, we
noticed that our approach was unable to infer the parallel mode in
some projects because these projects do not declare a static value in
some parameters (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parellel>}). For these projects,
it is required to inform additional parameters to enable the parallel
mode in the command line (\eg, \CodeIn{mvn test
-Dparallel.type=classesAndMethods}). \Jbc{We wouldn't have FALSE
NEGATIVES if we considered this $\rightarrow$}To handle this case, we
considered all valid values for the parameter.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\Luis{todo}\label{fig:rq5-answers}}
\end{figure}

@@

\subsection{Threats to Validity}

\Fix{Jean and Luis should write this. This is really important for an
  empirical study.  You need to undertand main sources of threat:
  internal, external, and construct.  Read this document for the
  basics: http://www.statsdirect.com/help/basics/validity.htm.  Read
  this document for an example:
  http://www.cin.ufpe.br/~damorim/publications/perez-etal-icst2017.pdf}

\subsection{Lessons Learned}

\Fix{Marcelo can write this...}

>>>>

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{llrrl}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 1.02x\\%
Medium & Apache \textbf{Flink} & 11.79m & 2.57m & 4.59x\\%
Long & Jenkins CI \textbf{Gerrit} Plugin & 51.19m & 40.31m &  1.26x\\%
Medium & Spotify \textbf{Helios} & 4.46m & 1.63m & 2.73x\\%  
Medium & \textbf{Javaslang} & 2.18m & 1.82m & 1.19x\\%
Medium & \textbf{Jcabi} GitHub & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
Medium & Apache \textbf{Log4J2} & 8.24m & 8.21m & 
    \cellcolor{lightgray}1.00x\\%
Medium & Jankotek \textbf{MapDB} & 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{total} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Abbreviation of project names appear in bold face
  and highest slowdown/speedup appear in gray color.}
\label{tab:speedup}
\end{figure}

@@

Research questions \numRQC{} and \numRQE{} investigate to which extent
parallelization is used in practice.  It is important to investigate
adoption as it is possible that developers may use alternative
mechanisms to execute tests.

\begin{itemize}
    \item \numRQC. \emph{\RQC}
\end{itemize}

To answer \numRQC{}, we selected all projects that ran in at least one
minute, \ie, projects from the \medg{} and \longg{} groups.  This set
includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
looked for dynamic and static manifestations of parallelism.
Section~\ref{sec:rqC-1} and~\ref{sec:rqC-2} report results for each of
these cases.

\vspace{1ex}
\subsubsection{Test execution with parallelism enabled by default}
\label{sec:rqC-1}

To find dynamic evidence of parallelism, we ran the test suites from
our set of \numMedLong{} projects to output all key-value pairs of
Maven parameters.  To that end, we used the option~\CodeIn{-X} to
produce debug output and the option~\CodeIn{-DskipTests} to skip
execution of tests.  We observed that only bootstrapping execution
suffices to discover which parallel configuration modes Maven will
actually use.  According to Maven's
documentation~\cite{maven-surefire-plugin}, any parallelism
configuration depends either on (1) the parameter \CodeIn{parallel} to
define the parallelism mode within a JVM followed by the parameter
\CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
  in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).  Large projects may contain several test suites
distributed on different Maven modules with different
configurations. In this case, we collect the Maven output from each
module discarding duplicates. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.

@@

\subsubsection{Presence of parallelism configurations in build files}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in
\emph{pom.xml} files\Comment{ in the same sample set of \numMedLong{}
  projects}. In principle, some projects can use parallel execution
although that is only activated when developers pass certain
parameters to the build process. For instance, it is possible to
create in Maven multiple configurations in the same build file and
select dynamically which one should be used.

\Mar{I have no clue what you mean here... Why should I care about
  space on build files?  I thought we did this check
  for every project and module.  $\rightarrow$}\Fix{To reduce the
  space of \Fix{x} build files, we considered a subset of \Fix{y}
  build files with the following criteria}: the given \pomf{} file has
\CodeIn{maven-surefire-plugin} plugin declaration and it has an
explicit \CodeIn{configuration} declaration. We automatically parsed
these \Fix{y} files and we used the same approach to classify the
parallelization mode from the parsed configurations as in our previous
analysis. In an initial analysis, we noticed that some projects do not
declare a static value in some parameters, instead, these projects
inform the actual value in the command line. To handle this case, we
computed all valid values for the parameter.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/survey.pdf}                                                                                                                                                   
     \caption{\Luis{todo}}
\end{figure}

@@
